Rule Synthesis for Network Intrusion Detectors

### 2020-06-04 paper/paper.tex
table 3 and 4

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 3 \\
    ICMP Info: Ping & 13 & 8 & 18 & 2 \\
    Dst/Host Unreachable & 132 & 6 & 3 & 1 \\
    Dst/Net Unreachable & 12 & 6 & 25 & 1 \\
    Dst/Port Unreachable & 3 & 6 & 12 & 1 \\
    ICMP Info: Echo Reply & 15 & 8 & 9 & 2 \\
    ICMP Info: Code 13 & 4 & 6 & 3 & 1 \\
    ICMP Info: Code 10 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 2\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 36 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 29\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1,881 & 1 \\
    Basebuilder LFI & 1 & 22 & 60,222 & 55 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 6 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}
  %\setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{0.5}
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
      UDP Teardrop & 3 & 5$\uparrow$ & 2 \cellcolor{lightgray}$\downarrow$ & 3 & 3 \\
    ICMP Info: Ping & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    Dst/Host Unreachable & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    Dst/Net Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    Dst/Port Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Echo Reply & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    ICMP Info: Code 13 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Code 10 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 2 & 2 & 2 & 7$\uparrow$ & 5$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 14$\uparrow$\\        
    JBoss JMX & 36 & 36 & 14\cellcolor{lightgray}$\downarrow$ & 34\cellcolor{lightgray}$\downarrow$ & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 15$\uparrow$ \\
    WeBid LFI & 29 & 29 & 72$\uparrow$ & 39$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 11$\uparrow$\\
    .idq access & 2  & 2 & 2 & 1\cellcolor{lightgray}$\downarrow$ & 15$\uparrow$ \\
    /system32/ in URI & 1  & 1 & 4$\uparrow$ & 1 & 15$\uparrow$\\
    Basebuilder LFI & 55  & 55 & 320$\uparrow$ & 112$\uparrow$ & 58$\uparrow$\\
      Tomcat Snoop Access & 6 & 6 & 3$\cellcolor{lightgray}\downarrow$ & 6 & 2,665$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 3 \\
    ICMP Info: Ping & 13 & 8 & 18 & 2 \\
    Dst/Host Unreachable & 132 & 6 & 3 & 1 \\
    Dst/Net Unreachable & 12 & 6 & 25 & 1 \\
    Dst/Port Unreachable & 3 & 6 & 12 & 1 \\
    ICMP Info: Echo Reply & 15 & 8 & 9 & 2 \\
    ICMP Info: Code 13 & 4 & 6 & 3 & 1 \\
    ICMP Info: Code 10 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 2\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 36 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 21\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1,881 & 1 \\
    Basebuilder LFI & 1 & 22 & 60,222 & 51 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 5 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[t!]
  \footnotesize
  \setlength{\tabcolsep}{8pt}
  %\setlength{\tabcolsep}{5pt}
  \renewcommand{\arraystretch}{0.5}
  \caption{\label{table:weights}Contribution of heuristic functions.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    base &
    -f1 &
    -f2 &    
    -f3 &
    -f4 \\
    \midrule
    Black Nurse & 2 & 7$\uparrow$ & 2 & 2 & 2 \\    
    Ping Scan & 2 &  8$\uparrow$& 2 & 2 & 2 \\
    SYN Flood & 1 & 1 & 1 & 1 & 1 \\
      UDP Teardrop & 3 & 5$\uparrow$ & 2 \cellcolor{lightgray}$\downarrow$ & 3 & 3 \\
    ICMP Info: Ping & 2 & 18$\uparrow$& 2 & 2 & 2 \\
    Dst/Host Unreachable & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    Dst/Net Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    Dst/Port Unreachable & 1 & 12$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Echo Reply & 2 & 9$\uparrow$ & 2 & 2 & 2 \\
    ICMP Info: Code 13 & 1 & 2$\uparrow$ & 1 & 1 & 1 \\
    ICMP Info: Code 10 & 1 & 3$\uparrow$ & 1 & 1 & 1 \\
    \midrule
    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 2 & 2 & 2 & 7$\uparrow$ & 6$\uparrow$ \\
    iisadmin access & 1  & 1 & 1 & 1 & 13$\uparrow$\\        
    JBoss JMX & 36 & 36 & 14\cellcolor{lightgray}$\downarrow$ & 34\cellcolor{lightgray}$\downarrow$ & 269$\uparrow$ \\
    scripttag & 1 & 1 & 3$\uparrow$ & 1 & 16$\uparrow$ \\
    WeBid LFI & 21 & 21 & 74$\uparrow$ & 39$\uparrow$ & 41$\uparrow$ \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 1  & 1 & 1 & 1 & 10$\uparrow$\\
    .idq access & 2  & 2 & 2 & 1\cellcolor{lightgray}$\downarrow$ & 14$\uparrow$ \\
    /system32/ in URI & 1  & 1 & 4$\uparrow$ & 1 & 14$\uparrow$\\
    Basebuilder LFI & 51  & 51 & 370$\uparrow$ & 112$\uparrow$ & 58$\uparrow$\\
      Tomcat Snoop Access & 5 & 5 & 2$\cellcolor{lightgray}\downarrow$ & 6 & 646$\uparrow$\\
    \bottomrule
  \end{tabular}
\end{table}
